---
output: word_document
---
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
## Read helper code
source("code/aaaInit.R")
show.res <- 'hide'  # options are 'asis' or 'hide'
```

```{r echo=FALSE, results='hide'}
sta <- read.csv("data/clean/stations.csv")

# Summarize depths & distances for nearshore cross-contour tows (82 & 84)
sta_ns <- filterD(sta,type=="nearshore")
sta_ns_begdep <- Summarize(~beg_depth,data=sta_ns)
sta_ns_enddep <- Summarize(~end_depth,data=sta_ns)
sta_ns_dist <- Summarize(~distance,data=sta_ns)
# Summarize depths for offshore along-contour tows (not 82 & 84)
sta_os <- filterD(sta,type=="offshore")
sta_os_avgdep <- Summarize(~avg_depth,data=sta_os)
sta_os_dist <- Summarize(~distance,data=sta_os)
```

The June tows were cross-contour with a mean beginning depth of `r formatC(sta_ns_begdep[["mean"]],format="f",digits=0)` m (range: `r formatC(sta_ns_begdep[["min"]],format="f",digits=0)`-`r formatC(sta_ns_begdep[["max"]],format="f",digits=0)`), ending depth of `r formatC(sta_ns_enddep[["mean"]],format="f",digits=0)` m (range: `r formatC(sta_ns_enddep[["min"]],format="f",digits=0)`-`r formatC(sta_ns_enddep[["max"]],format="f",digits=0)`), and distance covered of `r formatC(sta_ns_dist[["mean"]],format="f",digits=2)` km (range: `r formatC(sta_ns_dist[["min"]],format="f",digits=2)`-`r formatC(sta_ns_dist[["max"]],format="f",digits=2)`).  The tows in July followed a depth contour, had a mean average depth of `r formatC(sta_os_avgdep[["mean"]],format="f",digits=0)` m (range: `r formatC(sta_os_avgdep[["min"]],format="f",digits=0)`-`r formatC(sta_os_avgdep[["max"]],format="f",digits=0)`), and a mean distance covered of `r formatC(sta_os_dist[["mean"]],format="f",digits=2)` km (range: `r formatC(sta_os_dist[["min"]],format="f",digits=2)`-`r formatC(sta_os_dist[["max"]],format="f",digits=2)`).

```{r echo=FALSE, results=show.res}
reproInfo(addTOC=FALSE)
```
